---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
<!-- Use snippet 'render_markdown' for it -->

```{r,echo=FALSE}
knitr::opts_chunk$set(
  collapse=TRUE,
  comment="#>",
  fig.path="README-"
)
```

# vegtable2

<!-- badges: start -->
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/vegtable2)](https://cran.r-project.org/package=vegtable2)
<!-- badges: end -->

This is a package with functions for the internal use and adapted to own
purposes.
The functions included here are extensions to `taxlist`
([https://github.com/kamapu/taxlist](https://github.com/kamapu/taxlist)) and
`vegtable`
([https://github.com/kamapu/vegtable](https://github.com/kamapu/vegtable)) and
its functions may not work with any database.

## Updating to the last version of vegtable
The very first step is to install the package
[devtools](https://github.com/hadley/devtools) and dependencies.
Then you just need to execute following commands in your R-session:

```{r,eval=FALSE}
library(devtools)
install_github("kamapu/vegtable2")
```
